FoRTE baseline

### 2019-06-21 analysis/paper/paper.Rmd
[paper] Add submodel table to paper

@@

| Plant functional type | Species                 |
|-----------------------|-------------------------|
| Early hardwood        | _Betula papyrifera_     |
|                       | _Populus grandidentata_ |
|                       | _Populus tremuloides_   |
| Mid hardwood          | _Quercus rubra_         |
|                       | _Acer rubrum_           |
|                       | _Acer pensylvaticum_    |
| Late hardwood         | _Acer saccharum_        |
|                       | _Fagus grandifolia_     |
| Pine                  | _Pinus strobus_         |

>>>>

These sub-models are summarized in Table X.

| Name                         | Description                                                                          | Color                     |
|------------------------------|--------------------------------------------------------------------------------------|---------------------------|
| **Crown model**              |                                                                                      |                           |
| `closed` (default)           | Cohort crowns take up entire patch area. Competition for light based only on height. | Light                     |
| `finite`                     | Cohort crown area is proportional to DBH according to PFT-specific allometry.        | Dark                      |
| **Radiative transfer model** |                                                                                      |                           |
| `two-stream` (default)       | Two-stream approximation, as in CLM 4.5                                              | Primary (red, blue)       |
| `multi-scatter`              | Multiple-scatter approximation, following [@zhao_2005_multiple]                      | Secondary (green, orange) |
| **Trait plasticity**         |                                                                                      |                           |
| `static` (default)           | SLA and Vcmax are constant                                                           | Cool (blue, green)        |
| `plastic`                    | SLA increases, and Vcmax decreases, with light level                                 | Warm (red, orange)        |

@@

| Plant functional type | Species                 | Color  |
|-----------------------|-------------------------|--------|
| Early hardwood        | _Betula papyrifera_     | Violet |
|                       | _Populus grandidentata_ |        |
|                       | _Populus tremuloides_   |        |
| Mid hardwood          | _Quercus rubra_         | Blue   |
|                       | _Acer rubrum_           |        |
|                       | _Acer pensylvaticum_    |        |
| Late hardwood         | _Acer saccharum_        | Green  |
|                       | _Fagus grandifolia_     |        |
| Pine                  | _Pinus strobus_         | Yellow |
